Decentralized autonomous organization to automate governance\\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2016-04-19 paper/Paper.tex
Update WP and increase execute proposal period
- Increased the possible period after the voting deadline at which a
  proposal can be executed to 10 days.

- Added extra `if p.open` check to save gas

- Updated the whitepaper with the changes this PR introduces

\subsubsection*{emergenyCloseProposal}
This is used in the case `executeProposal` fails because it throws (e.g. when returuning the deposit, because the fallback function of this address throws, or when executing the proposed transaction). It can be called $5$ days after the voting deadline of the proposal passed. It will close the proposal.
\subsubsection*{splitDAO}
After a new Curator has been proposed, and the debating period in which the token holders could vote for or against the proposal has passed, this function is called by each of the DAO token holders that want to leave the current DAO and move to a new DAO with the proposed new Curator. This function creates a new DAO and moves a portion of the ether, as well as a portion of the reward tokens to the new DAO.
The arguments are:
\begin{description}
 \item[proposalID] The proposal ID.
 \item[newCurator] The address of the new Curator of the new DAO.
\end{description}
After a sanity check (see code), this function will create the new DAO if it hasn’t already been created using the contract \verb|daoCreator|, updates the split data stored in the proposal and stores the address of the new DAO in the split data.
This function moves the portion of ether that belongs to the caller of this function in the original DAO to the new DAO. This ether amount is denoted by $\Xi_{\text{sender}}$, stated in wei and is calculated as follows:
\begin{equation}
 \Xi_{\text{sender}} = \Xi_{\text{DAO}} \cdot T_{\text{sender}} / T_{\text{total}}
\end{equation}
Here $T_{\text{sender}}$ is the amount of tokens of the caller of the function and $\Xi_{\text{DAO}}$ is the balance of the DAO at the time of the split.
This will be used to effectively create tokens in the newly created DAO and fuel the new DAO just as the original DAO was fueled.
In addition to the ether which is moved to the new DAO, the reward tokens $R_{\text{sender}}$ are also transferred. 
They are calculated as follows:
\begin{equation}
 R_{\text{sender}} = R_{\text{DAO}} \cdot T_{\text{sender}} / T_{\text{total}}
\end{equation}
Where $R_{\text{DAO}}$ is the amount of reward tokens owned by the original DAO at the time of the split. These tokens allow the new DAO to retrieve their portion of the reward using the \verb|retrieveDAOReward| function of the original DAO.
At the end of this process all original DAO tokens of the sender account are destroyed. It is important to notice that in all integer division descirbed above, there may be remainders which stay with the DAO.

@@

    // The amount of days for which people who try to participate in the
    // creation by calling the fallback function will still get their ether back
    uint constant creationGracePeriod = 40 days;
    // The minimum debate period that a generic proposal can have
    uint constant minProposalDebatePeriod = 2 weeks;
    // The minimum debate period that a split proposal can have
    uint constant minSplitDebatePeriod = 1 weeks;
    // Period of days inside which it's possible to execute a DAO split
    uint constant splitExecutionPeriod = 27 days;
    // Period of time after which the minimum Quorum is halved
    uint constant quorumHalvingPeriod = 52 weeks;
    // Period after which a proposal can be closed
    // (used in the case `executeProposal` fails because it throws)
    uint constant executeProposalPeriod = 5 days;
    // Denotes the maximum proposal deposit that can be given. It is given as
    // a fraction of total Ether spent plus balance of the DAO
    uint constant maxDepositDivisor = 100;

@@

    /// @notice close the proposal (used in the case `executeProposal`
    /// fails because it throws)
    /// @param _proposalID The proposal ID
    function emergenyCloseProposal(uint _proposalID) external;

@@

        if (p.newCurator) {
            if (now > p.votingDeadline + splitExecutionPeriod) {
                p.open = false;
            }
            return;
        }

@@

    function emergenyCloseProposal(uint _proposalID) external {
        Proposal p = proposals[_proposalID];
        if (p.votingDeadline + executeProposalPeriod < now && p.open)
            closeProposal(_proposalID);
    }

>>>>

\subsubsection*{splitDAO}
After a new Curator has been proposed, and the debating period in which the token holders could vote for or against the proposal has passed, this function is called by each of the DAO token holders that want to leave the current DAO and move to a new DAO with the proposed new Curator. This function creates a new DAO and moves a portion of the ether, as well as a portion of the reward tokens to the new DAO.
The arguments are:
\begin{description}
 \item[proposalID] The proposal ID.
 \item[newCurator] The address of the new Curator of the new DAO.
\end{description}
After a sanity check (see code), this function will create the new DAO if it hasn’t already been created using the contract \verb|daoCreator|, updates the split data stored in the proposal and stores the address of the new DAO in the split data.
This function moves the portion of ether that belongs to the caller of this function in the original DAO to the new DAO. This ether amount is denoted by $\Xi_{\text{sender}}$, stated in wei and is calculated as follows:
\begin{equation}
 \Xi_{\text{sender}} = \Xi_{\text{DAO}} \cdot T_{\text{sender}} / T_{\text{total}}
\end{equation}
Here $T_{\text{sender}}$ is the amount of tokens of the caller of the function and $\Xi_{\text{DAO}}$ is the balance of the DAO at the time of the split.
This will be used to effectively create tokens in the newly created DAO and fuel the new DAO just as the original DAO was fueled.
In addition to the ether which is moved to the new DAO, the reward tokens $R_{\text{sender}}$ are also transferred. 
They are calculated as follows:
\begin{equation}
 R_{\text{sender}} = R_{\text{DAO}} \cdot T_{\text{sender}} / T_{\text{total}}
\end{equation}
Where $R_{\text{DAO}}$ is the amount of reward tokens owned by the original DAO at the time of the split. These tokens allow the new DAO to retrieve their portion of the reward using the \verb|retrieveDAOReward| function of the original DAO.
At the end of this process all original DAO tokens of the sender account are destroyed. It is important to notice that in all integer division descirbed above, there may be remainders which stay with the DAO.

@@

    // The amount of days for which people who try to participate in the
    // creation by calling the fallback function will still get their ether back
    uint constant creationGracePeriod = 40 days;
    // The minimum debate period that a generic proposal can have
    uint constant minProposalDebatePeriod = 2 weeks;
    // The minimum debate period that a split proposal can have
    uint constant minSplitDebatePeriod = 1 weeks;
    // Period of days inside which it's possible to execute a DAO split
    uint constant splitExecutionPeriod = 27 days;
    // Period of time after which the minimum Quorum is halved
    uint constant quorumHalvingPeriod = 52 weeks;
    // Period after which a proposal is closed
    // (used in the case `executeProposal` fails because it throws)
    uint constant executeProposalPeriod = 10 days;
    // Denotes the maximum proposal deposit that can be given. It is given as
    // a fraction of total Ether spent plus balance of the DAO
    uint constant maxDepositDivisor = 100;

@@

@@

        uint waitPeriod = p.newCurator
            ? splitExecutionPeriod
            : executeProposalPeriod;
        // If we are over deadline and waiting period, assert proposal is closed
        if (p.open && now > p.votingDeadline + waitPeriod) {
            closeProposal(_proposalID);
            return;
        }

@@
